Bird beak's elaboration and innovation

### 2022-08-08 Analysis/03-Elaboration_innovation_analysis.Rmd
Update 03-Elaboration_innovation_analysis.Rmd

```

@@

## Big list:
clade_info_passeriformes <- list(suborders = suborders,
                                 families = families)
## Save all that data
save(clade_info_passeriformes, file = "../Data/Processed/clade_info_passeriformes.rda")
```

>>>>

## Get the median elaboration/innovation for the groups
groups_median_EI <- list(
    "super_orders" = list("elaboration" = unlist(lapply(get.disparity(results$super_results_between$position, concatenate = FALSE), function(X) median(c(X)))),
                          "innovation"  = unlist(lapply(get.disparity(results$super_results_between$distance, concatenate = FALSE), function(X) median(c(X))))) ,
    "orders"       = list("elaboration" = unlist(lapply(get.disparity(results$order_results_between$position, concatenate = FALSE), function(X) median(c(X)))),
                          "innovation"  = unlist(lapply(get.disparity(results$order_results_between$distance, concatenate = FALSE), function(X) median(c(X)))))
)
save(groups_median_EI, file = "../Data/Processed/groups_median_EI.rda")
```

@@

## Big list:
clade_info_passeriformes <- list(suborders = suborders,
                                 families = families)
## Save all that data
save(clade_info_passeriformes, file = "../Data/Processed/clade_info_passeriformes.rda")

## Get the median elaboration/innovation for the groups
groups_median_EI_passeriformes <- list(
    "sub_orders" = list("elaboration" = unlist(lapply(get.disparity(results$suborder_results_between$position, concatenate = FALSE), function(X) median(c(X)))),
                          "innovation"  = unlist(lapply(get.disparity(results$suborder_results_between$distance, concatenate = FALSE), function(X) median(c(X))))) ,
    "families"       = list("elaboration" = unlist(lapply(get.disparity(results$family_results_between$position, concatenate = FALSE), function(X) median(c(X)))),
                          "innovation"  = unlist(lapply(get.disparity(results$family_results_between$distance, concatenate = FALSE), function(X) median(c(X)))))
)
save(groups_median_EI_passeriformes, file = "../Data/Processed/groups_median_EI_passeriformes.rda")
```
